%!TEX program = xelatex
\documentclass[11pt,a4paper]{article}

% Geometry
\usepackage[top=1.5cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry}

% Fonts
\usepackage{fontspec}
\setmainfont{Inter}[
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic,
]

% Colors
\usepackage{xcolor}
\definecolor{accent}{RGB}{34, 197, 94}
\definecolor{darkgray}{RGB}{55, 65, 81}
\definecolor{lightgray}{RGB}{107, 114, 128}

% Links
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=darkgray,
  urlcolor=darkgray,
  pdfauthor={Roman Vassilchenko},
  pdftitle={Roman Vassilchenko - Go Backend Developer},
}

% Lists
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.5em, itemsep=0.1em, parsep=0em, topsep=0.3em}

% Spacing
\usepackage{parskip}
\setlength{\parskip}{0.4em}
\setlength{\parindent}{0pt}

% Multi-column
\usepackage{multicol}

% Custom commands
\newcommand{\sectiontitle}[1]{%
  \vspace{0.6em}%
  {\large\bfseries #1}%
  \vspace{0.1em}%
  \textcolor{accent}{\hrule height 2pt}%
  \vspace{0.4em}%
}

\newcommand{\jobtitle}[4]{%
  \textbf{\MakeUppercase{#1}} \textit{#2} \hfill \textcolor{accent}{\textbf{#3}}\\
  {\small\textcolor{lightgray}{#4}}%
}

\newcommand{\techstack}[1]{%
  \vspace{0.2em}%
  {\small\colorbox{gray!10}{\textbf{Tech Stack}} #1}%
}

\newcommand{\contactitem}[1]{{\small #1}}

\begin{document}

\pagestyle{empty}

% Header
\begin{minipage}[t]{0.35\textwidth}
	\colorbox{accent}{\textcolor{white}{\small\textbf{\ Go Backend Developer\ }}}

	\vspace{0.5em}
	{\Huge\bfseries Roman\\Vassilchenko}

	\vspace{0.8em}
	\contactitem{+7 775 900-46-26}\\
	\contactitem{\href{mailto:roman.vassilchenko.work@gmail.com}{roman.vassilchenko.work@gmail.com}}\\
	\contactitem{\href{https://github.com/RomanVassilchenko}{github.com/RomanVassilchenko}}\\
	\contactitem{\href{https://linkedin.com/in/rovassilchenko}{linkedin.com/in/rovassilchenko}}\\
	\contactitem{\href{https://t.me/Roman_Vassilchenko}{t.me/Roman\_Vassilchenko}}
\end{minipage}%
\hfill%
\begin{minipage}[t]{0.60\textwidth}
	\vspace{1em}
	Go Backend Engineer with 2+ years of experience building high-load distributed systems. Designing and developing microservices that process millions of requests: event-driven architecture with Kafka, PostgreSQL optimization, gRPC/REST APIs. Currently at Bereke Bank building loan services with Camunda BPMN. Creator of AdalQarau — a procurement analytics platform with anomaly detection algorithms. Open to international relocation.
\end{minipage}

% Key Skills
\sectiontitle{Key Skills}

\colorbox{gray!10}{\textbf{Tech Stack}} Golang (2+ years), gRPC, REST/HTTP, PostgreSQL, Redis, Kafka, Docker, Camunda BPMN, MongoDB, Neo4j, Protocol Buffers (ProtoBuf), MinIO/S3, GitHub Actions, AWS, Kubernetes, testify, NixOS, Python.

% Work Experience
\sectiontitle{Work Experience}

\jobtitle{Middle Backend Go Developer}{Bereke Bank}{Sep 2024 — Present}{B2C Loan Request Platform \quad production; microservices; event-driven}
\begin{itemize}
	\item Developed and maintained \textbf{B2C loan-request microservices} for auto dealership credit processing.
	\item Integrated \textbf{Camunda BPMN workflows} for complex business process automation.
	\item Implemented \textbf{Kafka-based event-driven architecture} for real-time data processing.
	\item Created \textbf{Mattermost integration} for alerts and notifications across banking operations.
	\item Built internal procurement and loan-pledge systems supporting bank operations.
	\item Participated in digital transformation initiatives of core banking services.
\end{itemize}
\techstack{Go, PostgreSQL, Redis, Kafka, Camunda BPMN, Docker, CI/CD}

\vspace{0.5em}

\jobtitle{Junior Backend Go Developer}{Ozon Tech}{Aug 2024 — Sep 2024}{Enterprise Employee Portal (60,000+ users) \quad production; monolith → microservices}
\begin{itemize}
	\item Led monolith decomposition: extracted employee data into standalone service, reducing core load by \textbf{20–25\%}.
	\item Developed \textbf{staff-lib} — reusable library for DB access, validation, and middleware — adopted across dozens of services.
	\item Automated attendance enforcement: reclaiming unused seats and blocking repeat no-shows.
	\item Built data export pipeline from Ozon Forms to Vertica for analytics teams.
\end{itemize}
\techstack{Go, gRPC, PostgreSQL, ClickHouse, Redis, Kafka, Vertica}

\vspace{0.5em}

\jobtitle{Backend Developer Intern}{Ozon Tech}{Dec 2023 — Aug 2024}{Ozon Matrix Platform (Company-wide Hiring System) \quad production; microservices; high traffic}
\begin{itemize}
	\item Promoted from Intern to Junior Developer within 8 months.
	\item Optimized complex SQL queries, accelerating candidate list generation by up to \textbf{8×}.
	\item Re-engineered ElasticSearch filter logic — improved speed \textbf{2.5×} and reduced cluster load.
	\item Integrated Chatzone (Mattermost) via dedicated gRPC notification service with sharding and delayed Kafka dispatch — cut manager response time to applications.
	\item Designed Grafana dashboards for proactive error monitoring — boosted anomaly detection and response speed.
\end{itemize}
\techstack{Go, PostgreSQL, Redis, ElasticSearch, Kafka, ClickHouse, gRPC, REST}

% Education
\sectiontitle{Education}

\jobtitle{M.Sc. in Software Engineering}{Astana IT University (AITU), Astana}{2023 — 2027}{}
\begin{itemize}
	\item \textbf{Relevant Coursework:} Graph Theory Methods in Information Systems (Neo4j + GDS), Advanced Database Systems (PostgreSQL optimization), NoSQL Systems (MongoDB + FastAPI).
\end{itemize}

\vspace{0.3em}

\jobtitle{Previous Studies}{ITMO University, St. Petersburg}{2021 — 2023}{}
\begin{itemize}
	\item 2 years completed before transfer to AITU.
\end{itemize}

% Two columns for Additional and Languages
\vspace{0.3em}
\begin{minipage}[t]{0.48\textwidth}
	\sectiontitle{Additional}
	\begin{itemize}
		\item Full-time availability (on-site / hybrid / remote).
		\item Open to international relocation (Cyprus, Spain, Serbia, Kazakhstan).
		\item Seeking challenging backend engineering roles with growth opportunities.
	\end{itemize}
\end{minipage}%
\hfill%
\begin{minipage}[t]{0.48\textwidth}
	\sectiontitle{Languages}
	\begin{itemize}
		\item Russian — Native
		\item English — B2-C1 (Professional working proficiency)
		\item Kazakh — Basic
	\end{itemize}
\end{minipage}

% Key Projects
\sectiontitle{Key Projects}

\jobtitle{Creator}{AdalQarau — Public Procurement Analytics Platform}{2024 — Present}{}
\begin{itemize}
	\item Designed and built risk scoring system with graph-based relationship analysis between procurement participants.
	\item Scalable Go backend: data processing pipelines, risk indicators, automated report generation.
\end{itemize}
\techstack{Go, PostgreSQL, Kafka, REST API, Data Pipelines}

\end{document}
